%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for STAT 547C final project
% Author: Ben Bloem-Reddy <benbr@stat.ubc.ca>
% Date: Oct. 18, 2019
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Note: You will get an empty bibliography warning when compiling until you include a citation.

\documentclass[10pt]{article}
\input{header}
\input{defs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% your title/author/date information go here
\title{Probabilistic equivariance and convolutional neural networks} % replace with your title
\author{Sean La} % replace with your name

\bibliography{../../ref/STAT_547C.bib} % add the title of your bibliography file

% start of document
\begin{document}

\maketitle

% background section
\include{sections/background}

% add your main body sections here
\section{Sufficient conditions for convolution structure of $Y = f(\eta,X)$}
In this section, we show that equivariant $Y = f(\eta,X)$ being linear in its second argument almost surely, so that
$$
	f(\eta, a_1X_1 + a_2X_2) = a_1f(\eta,X_1) + a_2f(\eta,X_2),
$$
implies that $Y$ is a convolution of $X$,
$$
	Y \equas X * \chi(\eta)
$$
for some function $\chi(\eta)$. \footnote{Edit 14 December 2019: added homogeneity of scalar multiplication in definition of linearity}

First, we define what it means for a function to be \textit{linear}.
\begin{definition} \label{def:linear}\footnote{Edit 14 December 2019: added homogeneity of scalar multiplication in definition of linearity, and clarified $E$ and $F$ should be vector spaces over the same field.}
	Let $E$ and $F$ be vector spaces on the same field $\mathcal{F}$.	
	A function $h: E \to F$ is linear if for $x_1, x_2 \in E$ and $a_1, a_2 \in \mathcal{F}$, we have
	$$
		h(a_1x_1 + a_2x_2) = a_1h(x_1) + a_2h(x_2).
	$$ 
\end{definition}

\noindent

Now, the main contribution of this project follows.

\begin{theorem} \label{thm:convolution}
	Consider random vectors $(X,Y)$ with index sets $\mathcal{I}_X$ and $\mathcal{I}_Y$ and a compact group $G$ which acts on $\mathcal{I}_X$ and $\mathcal{I}_Y$.
	Moreover, suppose that $P_{X,Y}$ is $G$-equivariant.
	Lastly, suppose that the action of $G$ on both $\mathcal{I}_X$ and $\mathcal{I}_Y$ is transitive.
	Then if, conditioned on $X$, $Y \equas f(\eta, X)$ is a linear function almost surely (i.e. for some almost sure subset of the range of $\eta$), then $Y \equas X * \chi(\eta)$ in the sense of definition \ref{def:convolution}.
	More generally, $(X,Y) \equas (X,X * \chi(\eta))$.
\end{theorem}
\begin{proof}
Let $F(X) = f(\eta, X)$ be some realization of $Y$ so that $F(\cdot) = f(\eta, \cdot)$ is linear and $gY \equas f(\eta,gX)$ (the set of all such realizations has probability one since $f(\eta, \cdot)$ is linear almost surely and $gY \equas f(\eta,gX)$).
We prove this theorem by constructing an appropriate MFF-NN as in definition \ref{def:nn}, and then invoking theorem \ref{thm:gcnn}.

We may consider $X$ to be a function of its index set so that $X(i)$ gives the value of $X$ at component $i$ for $i \in \mathcal{I}_X$.
Likewise, we view $Y$ as a function of its index set $\mathcal{I}_{Y}$ in the same way.
Then the linear function $F$ can be seen as a function from the space of functions on $\mathcal{I}_{X}$ to the space of functions on $\mathcal{I}_Y$.
Lastly, we set the function $\sigma$ to be simply the identity function.
Then we define our MFF-NN $\mathcal{N}$ by the sequence of maps
$$
	X := f_0 \mapsto f_1 =: F(X) = Y
$$
where
$$
	Y(i) = F(X)(i) = \sigma(F(X)(i)).
$$
for $i \in \mathcal{I}_Y$.
Clearly, this construction matches the description of a MFF-NN given in definition \ref{def:nn}.

Now, define the action of group $G$ on $X$ to be the action of $G$ on its index set, so that
$$
	gX := \bbT_g(X) := X(gi)
$$
for $i \in \mathcal{I}_{X}$ and $g \in G$.
Similarly, define the action of $G$ on $Y$ as the action of $G$ on the its index set $\mathcal{I}_Y$, so that
$$
	gY := \bbT'_g(Y) = Y(g i)
$$
for $i \in \mathcal{I}_{Y}$ and $g \in G$.
By assumption, we have
$$
	\bbT'_g(Y) = gY = F(gX) = F(\bbT_g(X))
$$
for all $g \in G$ since $P_{X,Y}$ is $G$-equivariant.
Therefore, the layer of $\mathcal{N}$ is equivariant under the action of $G$.

Because the actions of $G$ on both $\mathcal{I}_{X}$ and $\mathcal{I}_{Y}$ are transitive, we may identify the index sets of $X$ and $Y$ by quotient groups $G/G_x$ and $G/G_y$, where $G_x$ and $G_y$ are the stabilizer subgroups of elements chosen to be the origins of $\mathcal{I}_X$ and $\mathcal{I}_Y$, respectively.

Therefore, by theorem \ref{thm:gcnn}, our MFF-NN $\mathcal{N}$ is a $G$-CNN so that
$$
	F(X) = X * \chi
$$
for some filter function $\chi$.
Letting the value of $\eta$ to vary over the subset of its range that gives $f(\eta,X)$ to be linear in $X$, it is easy to see that
$$
	f(\eta,X) = X * \chi(\eta).
$$
Take $\Omega_0 \subseteq \Omega$ such that $f(\eta,X)$ is both linear and equivariant under the action of $G$.
Because every $\omega \in \Omega_0$ gives that $Y(\omega) = X(\omega) * \chi(\eta(\omega))$ and $\P(\Omega_0) = 1$, we have
$$
	(X,Y) \equas (X,X * \chi(\eta))
$$
which finishes the proof.
\end{proof}

\subsection{Theorem \ref{thm:convolution} in terms of matrix multiplication}
We can also formulate theorem \ref{thm:convolution} in the language of matrix multiplication.
We have the following result in linear algebra:
\begin{proposition} \label{prop:linear}
Suppose $V_1$ and $V_2$ are finite dimensional vector spaces over the same field.
A transformation $T: V_1 \to V_2$ is linear if and only if it can be represented as a matrix; that is, for any vector $v \in V_1$, we have
$$
	T(v) = Mv
$$
for some matrix $M$ with column space in $V_2$.
\end{proposition}
Theorem \ref{thm:convolution} assumes that $f(\eta, X)$ is a linear mapping between the vector spaces in which $X$ and $Y$ lie.
Therefore, proposition \ref{prop:linear} implies that we can write
$$
	Y \equas M(\eta) X
$$
where $M(\eta)$ is a random matrix depending on $\eta$.
This holds true even if $Y \equas X * \chi(\eta)$, as we can express the filter $\chi(\eta)$ of a convolution as a matrix $M(\eta)$, so that
$$
	Y \equas X * \chi(\eta) = M(\eta)X.
$$
% open questions section
\include{sections/open-questions}

%%%% appendix
\clearpage
\appendix

% exercises and problems
\include{sections/appx-exercises}

% any other appendix sections


% bibliography
\printbibliography

\end{document}